---
title: "dcc_load_and_explore"
date: "today"
author: "Avihay Cohen"
format:
  html:
    self-contained: true
editor: source
---

```{r setup, echo=FALSE}

Sys.setenv(LANG = "EN")  # Set environment language to English

if (!requireNamespace("pacman", quietly = TRUE)) install.packages("pacman")
library(pacman)
pacman::p_load(tidyverse, DT, patchwork, RColorBrewer, here, tcltk, networkD3, lubridate)

save_cr <- function(..., file) {
  dir_path <- dirname(file)
  if (!dir.exists(dir_path)) {
    dir.create(dir_path, recursive = TRUE)
  }
  save(..., file = file)
} # wrapper for save() with automatic directory creation

save_rds_cr <- function(object, file) {
  dir_path <- dirname(file)
  
  if (!dir.exists(dir_path)) {
    dir.create(dir_path, recursive = TRUE)
  }
  
  saveRDS(object, file = file)
} # wrapper for saveRDS() with automatic directory creation

write_csv_cr <- function(x, file, ...) {
  dir_path <- dirname(file)
  if (!dir.exists(dir_path)) {
    dir.create(dir_path, recursive = TRUE)
  }
  write.csv(x, file = file, ...)
} # wrapper for write.csv() with automatic directory creation

```

# Data Citation Corpus (DCC) Loading, Cleaning and Overview

## 1. (DCC) Loading and initial exploration

<br>

The DCC (v4.1) was downloaded as a list of csv files that were then combined into one .rds object.

The DCC was then explored to find:

1.  Relevant columns' names

2.  Missing values

3.  Errors in publication dates

The Chunk below lets the user choose a folder with the downloaded csv files and combine them into one RData object.

```{r Loading and cleaning}

# 1. Loading and cleaning the DCC list (v4.1) ---------------------------------------------------------

# DCC data dictionary can be found here:
# https://zenodo.org/records/16901115

# Uncomment when running chunk independently:
# selected_dir <- selectDirectory(caption = "Select a Directory") # select DCC csv files directory

# Check if directory is already set
if (!exists("selected_dir")) {
  # Try to select a directory
  selected_dir <- tryCatch({
    tclvalue(tkchooseDirectory(title = "Please select a directory containing DCC corpus csv files"))
  }, error = function(e) {
    stop("No directory selected or selection was cancelled!")
  })
  
  if (nchar(selected_dir) == 0) {
    stop("Directory selection was cancelled!")
  }
}

# Let user choosee folder with csv files
message("Selected directory: ", selected_dir)

# Set wd
setwd(selected_dir)

# Get a list of all CSV files in the directory
file_list <- list.files(pattern = "*.csv")

# Read all CSV files into a list of data frames
data_list <- lapply(file_list, read.csv)

# Combine the list of data frames into a single data frame
DCC_corpus_orig <- bind_rows(data_list)

# Save DCC as .rds object
save_rds_cr(DCC_corpus_orig, file = file.path(here(
  "data",
  "raw",
  "dcc",
  "DCC_corpus_v41_orig.rds")))

DCC_corpus <- DCC_corpus_orig # assign _orig to a new variable

rm(data_list, file_list) # clean up
```

<br>

### 1.1 DCC Data Dictionary

<br>

**Table 1.** Below shows the relevant columns for the analysis and their description.

<br>

#### Table 1. DCC Data dictionary

<br>

```{r DCC data dictionary}

# Create data dictionary table
dcc_cols_dict <- tibble(
  Column_name = c(
    "publication",         
    "publishedDate",
    "dataset",
    "repository",
    "publisher",      
    "journal"
  ),
  Description = c(
    "Citing paper's DOI",
    "of citing paper",
    "Data identifier (=doi) or accession number (cited dataset)",
    "of cited dataset",
    "of citing paper",
    "of citing paper"
  )
)

# Render table

datatable(
  dcc_cols_dict, 
  options = list(
    pageLength = -1,  # display all entries by default
    scrollY = "200px",  # enable vertical scrolling
    scrollX = TRUE,     # enable horizontal scrolling for both content and header
    lengthMenu = list(c(-1, 5, 10, 25, 50), c("All", 5, 10, 25, 50)),
    dom = 'Bfrtip',
    buttons = c('csv')
    ),
  extensions = 'Buttons'
  )
```