---
title: "Results"
author: "Avihay Cohen"
format: html
editor: source
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}

# Load libraties

if (!requireNamespace("pacman", quietly = TRUE)) install.packages("pacman")
library(pacman)
pacman::p_load(tidyverse, DT, patchwork, RColorBrewer, here, tcltk, networkD3, htmlwidgets, ggvenn, ggbeeswarm, ggforce, glue, broom, scales, tibble, grid, purrr)

```

```{r prep, echo=FALSE, warning=FALSE, include=FALSE, message=FALSE}
#| message: false
#| warning: false

# choose_output_and_load_results.R

choose_output_and_load_results <- function() {
  output_dir <- tcltk::tk_choose.dir(caption = "Select the output folder")

  if (is.na(output_dir) || !nzchar(output_dir)) {
    stop("No folder was selected.", call. = FALSE)
  }

  output_dir <- normalizePath(output_dir, winslash = "/", mustWork = TRUE)
  derived_dir <- file.path(output_dir, "derived")

  paths <- c(
    all_sources_dcc_joined_dedup_condensed_dist =
      file.path(
        output_dir,
        "openalex_script_output",
        "all_sources_dcc_joined_condensed_dist_w_au_year_au_ov_no_shared_doi.rds"
      ),
    all_sources_dcc_joined_condensed =
      file.path(
        derived_dir,
        "all_sources_dcc_joined",
        "all_sources_dcc_joined_condensed.rds"
      ),
    datastet_cleaning_steps_13_rm_trailing_slash =
      file.path(
        derived_dir,
        "datastet",
        "cleaning_steps",
        "datastet_cleaning_steps_13_rm_trailing_slash.rds"
      ),
    oddpub_cleaning_steps_13_rm_trailing_slash =
      file.path(
        derived_dir,
        "oddpub",
        "cleaning_steps",
        "oddpub_cleaning_steps_13_rm_trailing_slash.rds"
      ),
    roagg_cleaning_steps_13_rm_trailing_slash =
      file.path(
        derived_dir,
        "roagg",
        "cleaning_steps",
        "roagg_cleaning_steps_13_rm_trailing_slash.rds"
      )
  )

  missing_paths <- paths[!file.exists(paths)]

  if (length(missing_paths) > 0L) {
    stop(
      paste0(
        "The following required file(s) were not found:\n",
        paste(names(missing_paths), missing_paths, sep = ": ", collapse = "\n")
      ),
      call. = FALSE
    )
  }

  all_sources_dcc_joined_dedup_condensed_dist <-
    readRDS(paths[["all_sources_dcc_joined_dedup_condensed_dist"]])

  all_sources_dcc_joined_condensed <-
    readRDS(paths[["all_sources_dcc_joined_condensed"]])

  datastet_cleaning_steps_13_rm_trailing_slash <-
    readRDS(paths[["datastet_cleaning_steps_13_rm_trailing_slash"]])

  oddpub_cleaning_steps_13_rm_trailing_slash <-
    readRDS(paths[["oddpub_cleaning_steps_13_rm_trailing_slash"]])

  roagg_cleaning_steps_13_rm_trailing_slash <-
    readRDS(paths[["roagg_cleaning_steps_13_rm_trailing_slash"]])

  objects_to_load <- list(
    output_dir = output_dir,
    derived_dir = derived_dir,
    all_sources_dcc_joined_dedup_condensed_dist =
      all_sources_dcc_joined_dedup_condensed_dist,
    all_sources_dcc_joined_condensed =
      all_sources_dcc_joined_condensed,
    datastet_cleaning_steps_13_rm_trailing_slash =
      datastet_cleaning_steps_13_rm_trailing_slash,
    oddpub_cleaning_steps_13_rm_trailing_slash =
      oddpub_cleaning_steps_13_rm_trailing_slash,
    roagg_cleaning_steps_13_rm_trailing_slash =
      roagg_cleaning_steps_13_rm_trailing_slash
  )

  list2env(objects_to_load, envir = .GlobalEnv)

  message("Loaded 5 input tables.")

  invisible(objects_to_load)
}

choose_output_and_load_results()

```

<br>

```{r matched_ds, echo=FALSE, warning=FALSE, message=FALSE}

flow_data <- all_sources_dcc_joined_dedup_condensed_dist

source_levels <- c("ODDPub", "ROAGG", "DataStet")

# Edit this tibble to control rectangle position, size, fill, outline, and text color
node_style <- tibble::tribble(
  ~source,       ~x, ~y, ~width, ~height, ~fill,      ~outline, ~outline_width, ~text_colour,
  "ODDPub",       1,  3,    2.4,    1.15, "#DDEBF7",  "black",             0.8, "black",
  "ROAGG",        4,  3,    2.4,    1.15, "#E2F0D9",  "black",             0.8, "black",
  "DataStet",     7,  3,    2.4,    1.15, "#FCE4D6",  "black",             0.8, "black",
  "all_sources",  4,  1,    3.6,    1.35, "#FFF2CC",  "black",             0.8, "black"
)

# Edit these to control all arrows
arrow_colour <- "black"
arrow_linewidth <- 0.8
arrow_linetype <- 1
arrow_angle <- 20
arrow_length <- grid::unit(0.25, "cm")

count_flow_metric <- function(data, distinct_cols, source_levels = c("ODDPub", "ROAGG", "DataStet")) {
  source_counts <- tibble::tibble(source = source_levels) |>
    dplyr::left_join(
      data |>
        dplyr::filter(source %in% source_levels) |>
        dplyr::distinct(source, dplyr::across(tidyselect::all_of(distinct_cols))) |>
        dplyr::count(source, name = "n"),
      by = "source"
    ) |>
    dplyr::mutate(
      n = dplyr::coalesce(n, 0L)
    )
  
  all_sources_sum <- sum(source_counts$n)
  
  all_sources_dedup <- data |>
    dplyr::filter(source %in% source_levels) |>
    dplyr::distinct(dplyr::across(tidyselect::all_of(distinct_cols))) |>
    nrow()
  
  tibble::tibble(
    source = c(source_levels, "all_sources"),
    n = c(source_counts$n, all_sources_sum),
    n_dedup = c(rep(NA_integer_, length(source_levels)), all_sources_dedup)
  )
}

make_flow_plot <- function(data, distinct_cols, metric_label, node_style, source_levels = c("ODDPub", "ROAGG", "DataStet")) {
  counts_tbl <- count_flow_metric(
    data = data,
    distinct_cols = distinct_cols,
    source_levels = source_levels
  )
  
  nodes <- node_style |>
    dplyr::left_join(counts_tbl, by = "source") |>
    dplyr::mutate(
      label = dplyr::case_when(
        source == "all_sources" ~ paste0(
          "All sources",
          "\n",
          metric_label,
          " Sum: ",
          n,
          "\n",
          metric_label,
          " Distinct Sum: ",
          n_dedup
        ),
        .default = paste0(
          source,
          "\n",
          metric_label,
          "",
          n
        )
      ),
      xmin = x - width / 2,
      xmax = x + width / 2,
      ymin = y - height / 2,
      ymax = y + height / 2
    )
  
  center_node <- nodes |>
    dplyr::filter(source == "all_sources") |>
    dplyr::slice(1)
  
  edges <- nodes |>
    dplyr::filter(source %in% source_levels) |>
    dplyr::transmute(
      source,
      x = x,
      y = ymin,
      xend = center_node$x[[1]],
      yend = center_node$ymax[[1]]
    )
  
  ggplot2::ggplot() +
    ggplot2::geom_rect(
      data = nodes,
      ggplot2::aes(
        xmin = xmin,
        xmax = xmax,
        ymin = ymin,
        ymax = ymax,
        fill = fill,
        colour = outline,
        linewidth = outline_width
      ),
      show.legend = FALSE
    ) +
    ggplot2::scale_fill_identity() +
    ggplot2::scale_linewidth_identity() +
    ggplot2::geom_text(
      data = nodes,
      ggplot2::aes(
        x = x,
        y = y,
        label = label,
        colour = text_colour
      ),
      lineheight = 1.1,
      size = 4.2,
      show.legend = FALSE
    ) +
    ggplot2::scale_colour_identity() +
    ggplot2::geom_segment(
      data = edges,
      ggplot2::aes(
        x = x,
        y = y,
        xend = xend,
        yend = yend
      ),
      colour = arrow_colour,
      linewidth = arrow_linewidth,
      linetype = arrow_linetype,
      arrow = grid::arrow(
        angle = arrow_angle,
        length = arrow_length,
        type = "closed"
      )
    ) +
    ggplot2::coord_equal(
      xlim = c(min(nodes$xmin) - 0.4, max(nodes$xmax) + 0.4),
      ylim = c(min(nodes$ymin) - 0.4, max(nodes$ymax) + 0.4),
      clip = "off"
    ) +
    ggplot2::theme_void()
}

flow_data_unique_datasets_sources <- dplyr::bind_rows(
  oddpub_cleaning_steps_13_rm_trailing_slash |>
    dplyr::distinct(dataset_clean) |>
    dplyr::transmute(
      source = "ODDPub",
      dataset_clean
    ),
  roagg_cleaning_steps_13_rm_trailing_slash |>
    dplyr::distinct(dataset_clean) |>
    dplyr::transmute(
      source = "ROAGG",
      dataset_clean
    ),
  datastet_cleaning_steps_13_rm_trailing_slash |>
    dplyr::distinct(dataset_clean) |>
    dplyr::transmute(
      source = "DataStet",
      dataset_clean
    )
)

plot_unique_datasets_sources <- make_flow_plot(
  data = flow_data_unique_datasets_sources,
  distinct_cols = "dataset_clean",
  metric_label = "",
  node_style = node_style,
  source_levels = source_levels
)

plot_unique_datasets <- make_flow_plot(
  data = flow_data,
  distinct_cols = "dataset_clean",
  metric_label = "",
  node_style = node_style,
  source_levels = source_levels
)

# If your table still uses doi_source instead of doi_charite, change "doi_charite" below to "doi_source"
plot_unique_doi_charite <- make_flow_plot(
  data = flow_data,
  distinct_cols = "doi_charite",
  metric_label = "",
  node_style = node_style,
  source_levels = source_levels
)

plot_unique_mentions <- make_flow_plot(
  data = flow_data,
  distinct_cols = c("doi_dcc", "dataset_clean"),
  metric_label = "",
  node_style = node_style,
  source_levels = source_levels
)

```

<br>

# Number of Datasets by Source

**Note:** for ROAGG and Datastet, some datasets are _not_ Open-data/Restricted

```{r plot_sources_ds, echo=FALSE, warning=FALSE, message=FALSE}

plot_unique_datasets_sources

```

# Number of Matched Datasets by Source

```{r plot_matched_ds, echo=FALSE, warning=FALSE, message=FALSE}

plot_unique_datasets

```

# Number of Articles Associated with Matched Datasets by Source

```{r plot_matched_dois, echo=FALSE, warning=FALSE, message=FALSE}

plot_unique_doi_charite

```

# Number of Mentions by Source

```{r plot_matched_mentions, echo=FALSE, warning=FALSE, message=FALSE}

plot_unique_mentions


```

<br>

# Distribution Frequency of Datasets References

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#| label: fig-datasets-freq-dist
#| out.width: 100%

ds_freq <- all_sources_dcc_joined_dedup_condensed_dist |> 
  select(dataset_clean, doi_dcc) |> 
  distinct() |> 
  group_by(dataset_clean) |> 
  summarise(n=n()) |>
  arrange(dataset_clean, n)

ds_freq_plot_data <- ds_freq |>
  dplyr::filter(!is.na(n), n > 0)

bins_n <- ds_freq_plot_data |>
  dplyr::summarise(
    bins = grDevices::nclass.FD(log10(n)),
    bins = dplyr::coalesce(as.integer(round(bins)), 1L),
    bins = pmax(5L, pmin(bins, 20L))
  ) |>
  dplyr::pull(bins)

x_breaks <- scales::breaks_log(n = 6)(range(ds_freq_plot_data$n))

hist_counts <- ggplot2::ggplot_build(
  ggplot2::ggplot(ds_freq_plot_data, ggplot2::aes(x = n)) +
    ggplot2::geom_histogram(bins = bins_n)
)$data[[1]]$count

fig_width <- pmin(12, pmax(7, 5.5 + 0.18 * bins_n))
fig_height <- pmin(10, pmax(5, 4.5 + 0.12 * max(hist_counts)))

knitr::opts_current$set(
  fig.width = fig_width,
  fig.height = fig_height
)

ds_freq_plot_data |>
  ggplot2::ggplot(ggplot2::aes(x = n)) +
  ggplot2::geom_histogram(
    bins = bins_n,
    colour = "black",
    fill = NA
  ) +
  ggplot2::stat_bin(
    bins = bins_n,
    geom = "text",
    ggplot2::aes(label = after_stat(count)),
    vjust = -0.3,
    size = 4
  ) +
  ggplot2::scale_x_log10(
    breaks = x_breaks,
    labels = scales::label_number(accuracy = 1)
  ) +
  ggplot2::scale_y_continuous(
    breaks = scales::breaks_pretty(n = 6),
    expand = ggplot2::expansion(mult = c(0, 0.08))
  ) +
  ggplot2::labs(
    x = "Number of References (log scale)",
    y = "Number of Datasets"
  ) +
  ggplot2::theme_classic() +
  ggplot2::theme(
    legend.position = "none",
    axis.title.y = ggplot2::element_text(
      size = 24,
      color = "black",
      margin = ggplot2::margin(r = 20)
    ),
    axis.title.x = ggplot2::element_text(
      size = 24,
      color = "black",
      margin = ggplot2::margin(t = 20)
    ),
    axis.text.y = ggplot2::element_text(size = 22, color = "black"),
    axis.text.x = ggplot2::element_text(size = 22, color = "black")
  )

```

# Distribution of Mentions Across Repositories

```{r repo-dist-ds, echo=FALSE, warning=FALSE, message=FALSE}
#| label: repo-dist-ds
#| out.width: 80%

shorten_repository_label <- function(x, max_chars = 30) {
  tibble::tibble(repository_dcc = x) |>
    dplyr::mutate(
      inside_parens = stringr::str_match(repository_dcc, "\\(([^()]*)\\)")[, 2],
      has_parens = !is.na(inside_parens),
      parens_has_space = has_parens & stringr::str_detect(inside_parens, "\\s"),
      parens_no_space = has_parens & !parens_has_space & inside_parens != "",
      outside_parens = repository_dcc |>
        stringr::str_remove("\\s*\\([^()]*\\)") |>
        stringr::str_squish(),
      first_token = stringr::str_extract(repository_dcc, "\\S+"),
      repository_label = dplyr::case_when(
        nchar(repository_dcc) <= max_chars ~ repository_dcc,
        parens_no_space ~ inside_parens,
        parens_has_space & outside_parens != "" ~ outside_parens,
        .default = first_token
      )
    ) |>
    dplyr::pull(repository_label)
}

rep_dt <- all_sources_dcc_joined_dedup_condensed_dist |>
  select(repository_dcc, doi_dcc, dataset_clean) |>
  group_by(repository_dcc) |>
  summarise(n = n_distinct(doi_dcc, dataset_clean), .groups = "drop") |>
  arrange(desc(n))

rep_dt_plot_data <- rep_dt |>
  dplyr::filter(!is.na(n), n > 0) |>
  dplyr::mutate(
    repository_label = shorten_repository_label(repository_dcc, max_chars = 30)
  )

label_map <- stats::setNames(
  rep_dt_plot_data$repository_label,
  rep_dt_plot_data$repository_dcc
)

n_repos <- nrow(rep_dt_plot_data)

max_repo_chars <- rep_dt_plot_data |>
  summarise(
    max_repo_chars = max(c(nchar(as.character(repository_label)), 0), na.rm = TRUE)
  ) |>
  pull(max_repo_chars)

max_value_digits <- rep_dt_plot_data |>
  summarise(
    max_value_digits = max(c(nchar(as.character(n)), 1), na.rm = TRUE)
  ) |>
  pull(max_value_digits)

y_breaks <- scales::breaks_log(n = 7)(range(c(rep_dt_plot_data$n, 1), na.rm = TRUE))

top_expand <- pmin(
  0.35,
  pmax(0.15, 0.10 + 0.02 * max_value_digits)
)

fig_height <- pmin(
  18,
  pmax(5, 2.8 + 0.32 * n_repos)
)

fig_width <- pmin(
  16,
  pmax(8, 6.5 + 0.05 * max_repo_chars + 0.35 * max_value_digits)
)

knitr::opts_current$set(
  fig.width = fig_width,
  fig.height = fig_height
)

rep_dt_plot_data |>
  ggplot(aes(x = reorder(repository_dcc, n), y = n)) +
  geom_bar(
    stat = "identity",
    position = "dodge",
    fill = "#80CBC4"
  ) +
  geom_text(
    aes(y = n, label = n),
    hjust = -0.2,
    size = 5,
    color = "black"
  ) +
  scale_x_discrete(labels = label_map) +
  scale_y_log10(
    breaks = y_breaks,
    labels = scales::label_comma(),
    expand = expansion(mult = c(0.02, top_expand))
  ) +
  coord_flip() +
  labs(
    x = "Repository",
    y = "Number of Mentions (Log Scale)"
  ) +
  theme_classic() +
  theme(
    legend.position = "none",
    axis.title.y = element_text(size = 14, color = "black", margin = margin(r = 20)),
    axis.title.x = element_text(size = 14, color = "black", margin = margin(t = 20)),
    axis.text.y = element_text(size = 12, color = "black"),
    axis.text.x = element_text(size = 12, color = "black"),
    panel.grid.major.x = element_line(color = "gray80", linewidth = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank()
  )

```

# Distribution of Datasets Across Repositories

```{r repo-dist-ref, echo=FALSE, warning=FALSE, message=FALSE}
#| label: repo-dist-ref
#| out.width: 80%

shorten_repository_label <- function(x, max_chars = 30) {
  tibble::tibble(repository_dcc = x) |>
    dplyr::mutate(
      inside_parens = stringr::str_match(repository_dcc, "\\(([^()]*)\\)")[, 2],
      has_parens = !is.na(inside_parens),
      parens_has_space = has_parens & stringr::str_detect(inside_parens, "\\s"),
      parens_no_space = has_parens & !parens_has_space & inside_parens != "",
      outside_parens = repository_dcc |>
        stringr::str_remove("\\s*\\([^()]*\\)") |>
        stringr::str_squish(),
      first_token = stringr::str_extract(repository_dcc, "\\S+"),
      repository_label = dplyr::case_when(
        nchar(repository_dcc) <= max_chars ~ repository_dcc,
        parens_no_space ~ inside_parens,
        parens_has_space & outside_parens != "" ~ outside_parens,
        .default = first_token
      )
    ) |>
    dplyr::pull(repository_label)
}

rep_ds <- all_sources_dcc_joined_dedup_condensed_dist |>
  select(repository_dcc, dataset_clean) |>
  group_by(repository_dcc) |>
  summarise(n = n_distinct(dataset_clean), .groups = "drop") |>
  arrange(desc(n))

rep_ds_plot_data <- rep_ds |>
  dplyr::filter(!is.na(n), n > 0) |>
  dplyr::mutate(
    repository_label = shorten_repository_label(repository_dcc, max_chars = 30)
  )

label_map <- stats::setNames(
  rep_ds_plot_data$repository_label,
  rep_ds_plot_data$repository_dcc
)

n_repos <- nrow(rep_ds_plot_data)

max_repo_chars <- rep_ds_plot_data |>
  summarise(
    max_repo_chars = max(c(nchar(as.character(repository_label)), 0), na.rm = TRUE)
  ) |>
  pull(max_repo_chars)

max_value_digits <- rep_ds_plot_data |>
  summarise(
    max_value_digits = max(c(nchar(as.character(n)), 1), na.rm = TRUE)
  ) |>
  pull(max_value_digits)

y_breaks <- scales::breaks_log(n = 7)(range(c(rep_ds_plot_data$n, 1), na.rm = TRUE))

top_expand <- pmin(
  0.35,
  pmax(0.15, 0.10 + 0.02 * max_value_digits)
)

fig_height <- pmin(
  18,
  pmax(5, 2.8 + 0.32 * n_repos)
)

fig_width <- pmin(
  16,
  pmax(8, 6.5 + 0.05 * max_repo_chars + 0.35 * max_value_digits)
)

knitr::opts_current$set(
  fig.width = fig_width,
  fig.height = fig_height
)

rep_ds_plot_data |>
  ggplot(aes(x = reorder(repository_dcc, n), y = n)) +
  geom_bar(
    stat = "identity",
    position = "dodge",
    fill = "#80CBC4"
  ) +
  geom_text(
    aes(y = n, label = n),
    hjust = -0.2,
    size = 5,
    color = "black"
  ) +
  scale_x_discrete(labels = label_map) +
  scale_y_log10(
    breaks = y_breaks,
    labels = scales::label_comma(),
    expand = expansion(mult = c(0.02, top_expand))
  ) +
  coord_flip() +
  labs(
    x = "Repository",
    y = "Number of Distinct Datasets (Log Scale)"
  ) +
  theme_classic() +
  theme(
    legend.position = "none",
    axis.title.y = element_text(size = 14, color = "black", margin = margin(r = 20)),
    axis.title.x = element_text(size = 14, color = "black", margin = margin(t = 20)),
    axis.text.y = element_text(size = 12, color = "black"),
    axis.text.x = element_text(size = 12, color = "black"),
    panel.grid.major.x = element_line(color = "gray80", linewidth = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank()
  )


```

# Datasets References by Year: TOP 10 mentioned identifiers

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#| label: fig-top10-datasets-by-year
#| out.width: 100%

top_n_datasets <- 10L

top_datasets_overall <- all_sources_dcc_joined_dedup_condensed_dist |>
  dplyr::filter(!is.na(dataset_clean), dataset_clean != "", !is.na(doi_dcc), doi_dcc != "") |>
  dplyr::group_by(dataset_clean) |>
  dplyr::summarise(
    n_overall = dplyr::n_distinct(doi_dcc),
    .groups = "drop"
  ) |>
  dplyr::arrange(dplyr::desc(n_overall), dataset_clean) |>
  dplyr::slice_head(n = top_n_datasets)

desired_order <- top_datasets_overall$dataset_clean

year_dcc_dt_all_for_plot_top10 <- all_sources_dcc_joined_dedup_condensed_dist |>
  dplyr::filter(
    dataset_clean %in% desired_order,
    !is.na(publishedDate),
    !is.na(doi_dcc),
    doi_dcc != ""
  ) |>
  dplyr::mutate(
    year = readr::parse_number(stringr::str_sub(as.character(publishedDate), 1, 4))
  ) |>
  dplyr::filter(!is.na(year)) |>
  dplyr::group_by(year, dataset_clean) |>
  dplyr::summarise(
    count = dplyr::n_distinct(doi_dcc),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    dataset_clean = factor(dataset_clean, levels = desired_order),
    year = dplyr::case_when(
      year <= 2012 ~ "<=2012",
      .default = as.character(year)
    )
  )

year_levels <- year_dcc_dt_all_for_plot_top10 |>
  dplyr::distinct(year) |>
  dplyr::mutate(
    year_num = readr::parse_number(year),
    year_sort = dplyr::case_when(
      year == "<=2012" ~ -Inf,
      .default = year_num
    )
  ) |>
  dplyr::arrange(year_sort, year) |>
  dplyr::pull(year)

year_dcc_dt_all_for_plot_top10 <- year_dcc_dt_all_for_plot_top10 |>
  dplyr::mutate(
    year = factor(year, levels = year_levels)
  )

label_data_top10 <- year_dcc_dt_all_for_plot_top10 |>
  dplyr::mutate(
    label = as.character(count)
  )

n_years <- length(year_levels)

max_total_per_year <- year_dcc_dt_all_for_plot_top10 |>
  dplyr::group_by(year) |>
  dplyr::summarise(total = sum(count), .groups = "drop") |>
  dplyr::summarise(max_total = max(total, na.rm = TRUE)) |>
  dplyr::pull(max_total)

max_total_digits <- nchar(as.character(max_total_per_year))

fig_width <- pmin(
  18,
  pmax(8, 5.8 + 0.45 * n_years + 0.25 * max_total_digits)
)

fig_height <- pmin(
  12,
  pmax(6.5, 5.2 + 0.18 * top_n_datasets)
)

knitr::opts_current$set(
  fig.width = fig_width,
  fig.height = fig_height
)

year_dcc_dt_all_for_plot_top10 |>
  ggplot2::ggplot(
    ggplot2::aes(
      x = year,
      y = count,
      fill = factor(dataset_clean, levels = rev(desired_order))
    )
  ) +
  ggplot2::geom_col(position = "stack") +
  ggplot2::geom_text(
    data = label_data_top10,
    ggplot2::aes(
      x = year,
      y = count,
      label = label,
      fill = factor(dataset_clean, levels = rev(desired_order))
    ),
    position = ggplot2::position_stack(vjust = 0.5),
    size = 3.2,
    show.legend = FALSE
  ) +
  ggplot2::labs(
    x = "Publication Year of Referencing Article",
    y = "Number of References",
    fill = "Dataset"
  ) +
  ggplot2::scale_x_discrete(
    labels = \(x) dplyr::case_when(
      x == "<=2012" ~ "\u2264 2012",
      .default = x
    )
  ) +
  ggplot2::scale_y_continuous(
    breaks = scales::breaks_pretty(n = 6),
    expand = ggplot2::expansion(mult = c(0, 0.03))
  ) +
  ggplot2::scale_fill_manual(
    values = stats::setNames(
      grDevices::hcl.colors(length(desired_order), palette = "Set 3"),
      rev(desired_order)
    ),
    breaks = rev(desired_order)
  ) +
  ggplot2::theme_classic() +
  ggplot2::theme(
    axis.title.y = ggplot2::element_text(size = 20, color = "black", margin = ggplot2::margin(r = 20)),
    axis.title.x = ggplot2::element_text(size = 20, color = "black", margin = ggplot2::margin(t = 20)),
    axis.text.y = ggplot2::element_text(size = 14, color = "black"),
    axis.text.x = ggplot2::element_text(size = 14, color = "black", angle = 45, hjust = 1),
    legend.title = ggplot2::element_text(size = 20, margin = ggplot2::margin(b = 15)),
    legend.text = ggplot2::element_text(size = 16),
    legend.key.height = grid::unit(25, "pt"),
    legend.box.margin = ggplot2::margin(l = 16)
  )



```

# Sources of Identifiers

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#| label: fig-venn-ids
#| out.width: 100%

# Data
dat <- all_sources_dcc_joined_condensed

# ------------------------------------------------------------
# Order 1: ODDPub -> DataStet -> ROAGG
# ------------------------------------------------------------

oddpub <- dat |>
  dplyr::filter(source == "ODDPub") |>
  dplyr::distinct(dataset_clean)

datastet_new <- dat |>
  dplyr::filter(source == "DataStet") |>
  dplyr::distinct(dataset_clean) |>
  dplyr::anti_join(
    oddpub,
    by = "dataset_clean"
  )

roagg_new <- dat |>
  dplyr::filter(source == "ROAGG") |>
  dplyr::distinct(dataset_clean) |>
  dplyr::anti_join(
    dplyr::bind_rows(oddpub, datastet_new) |>
      dplyr::distinct(dataset_clean),
    by = "dataset_clean"
  )

counts_oddpub_datastet_roagg <- tibble::tibble(
  source = c("ODDPub", "DataStet", "ROAGG"),
  unique_contribution = c(
    nrow(oddpub),
    nrow(datastet_new),
    nrow(roagg_new)
  )
)

counts_oddpub_datastet_roagg


# ------------------------------------------------------------
# Order 2: ODDPub -> ROAGG -> DataStet
# ------------------------------------------------------------

oddpub <- dat |>
  dplyr::filter(source == "ODDPub") |>
  dplyr::distinct(dataset_clean)

roagg_new <- dat |>
  dplyr::filter(source == "ROAGG") |>
  dplyr::distinct(dataset_clean) |>
  dplyr::anti_join(
    oddpub,
    by = "dataset_clean"
  )

datastet_new <- dat |>
  dplyr::filter(source == "DataStet") |>
  dplyr::distinct(dataset_clean) |>
  dplyr::anti_join(
    dplyr::bind_rows(oddpub, roagg_new) |>
      dplyr::distinct(dataset_clean),
    by = "dataset_clean"
  )

counts_oddpub_roagg_datastet <- tibble::tibble(
  source = c("ODDPub", "ROAGG", "DataStet"),
  unique_contribution = c(
    nrow(oddpub),
    nrow(roagg_new),
    nrow(datastet_new)
  )
)

counts_oddpub_roagg_datastet


# All 7 mutually exclusive source combinations

dataset_overlap_counts <- dat |>
  dplyr::filter(source %in% c("ODDPub", "DataStet", "ROAGG")) |>
  dplyr::distinct(dataset_clean, source) |>
  dplyr::group_by(dataset_clean) |>
  dplyr::summarise(
    oddpub = "ODDPub" %in% source,
    datastet = "DataStet" %in% source,
    roagg = "ROAGG" %in% source,
    .groups = "drop"
  ) |>
  dplyr::mutate(
    overlap = dplyr::case_when(
      oddpub & !datastet & !roagg ~ "ODDPub only",
      !oddpub & datastet & !roagg ~ "DataStet only",
      !oddpub & !datastet & roagg ~ "ROAGG only",
      oddpub & datastet & !roagg ~ "ODDPub + DataStet only",
      oddpub & !datastet & roagg ~ "ODDPub + ROAGG only",
      !oddpub & datastet & roagg ~ "DataStet + ROAGG only",
      oddpub & datastet & roagg ~ "All three",
      .default = NA_character_
    ),
    overlap = factor(
      overlap,
      levels = c(
        "ODDPub only",
        "DataStet only",
        "ROAGG only",
        "ODDPub + DataStet only",
        "ODDPub + ROAGG only",
        "DataStet + ROAGG only",
        "All three"
      )
    )
  ) |>
  dplyr::count(overlap, name = "n_datasets") |>
  tidyr::complete(
    overlap,
    fill = list(n_datasets = 0)
  )

dataset_overlap_counts


# Plot

dat <- all_sources_dcc_joined_condensed |>
  dplyr::filter(source %in% c("ODDPub", "DataStet", "ROAGG")) |>
  dplyr::distinct(dataset_clean, source)

venn_sets <- list(
  ODDPub = dat |>
    dplyr::filter(source == "ODDPub") |>
    dplyr::pull(dataset_clean),

  DataStet = dat |>
    dplyr::filter(source == "DataStet") |>
    dplyr::pull(dataset_clean),

  ROAGG = dat |>
    dplyr::filter(source == "ROAGG") |>
    dplyr::pull(dataset_clean)
)

# Control circle fill colors here
venn_colors <- c(
  ODDPub = "#4C78A8",
  DataStet = "#F58518",
  ROAGG = "#54A24B"
)

ggvenn::ggvenn(
  venn_sets,
  fill_color = venn_colors[names(venn_sets)],
  fill_alpha = 0.4,
  stroke_size = 0.8,
  set_name_size = 5,
  text_size = 4,
  show_elements = FALSE,
  show_percentage = TRUE
) +
  ggplot2::labs(
    title = "Overlap of datasets across sources"
  ) +
  ggplot2::theme_void()


```